Figures

### 2025-02-25 Figures/PaperFiguresextended.Rmd
cleaned up code

Figure 1e, 2a, S3a
CODE running, need to extend the PCA analysis folder
dir_out <- "/home/common/data/output/projects/ENDO/E044/A072/allcells_EndoAtlas_SCTassay/"

@@

#Figure 2a
biplot(p,
    colby = 'MenstrualCyclePhase',
    # ellipse config
      ellipse = TRUE,
      ellipseType = 't',
      ellipseLevel = 0.90,
      ellipseFill = TRUE,
      ellipseAlpha = 1/4,
      ellipseLineSize = 1.0,
    labSize = 0,drawConnectors = FALSE,
    legendPosition = 'top', legendLabSize = 16, legendIconSize = 8.0)

@@

>>>>

Figure 1e, 2a
CODE running, need to extend the PCA analysis folder
dir_out <- "/home/common/data/output/projects/ENDO/E044/A072/allcells_EndoAtlas_SCTassay/"

@@

#Figure 2a
biplot(p,
    colby = 'MenstrualCyclePhase',
    # ellipse config
      ellipse = TRUE,
      ellipseType = 't',
      ellipseLevel = 0.90,
      ellipseFill = TRUE,
      ellipseAlpha = 1/4,
      ellipseLineSize = 1.0,
    labSize = 0,drawConnectors = FALSE,
    legendPosition = 'top', legendLabSize = 16, legendIconSize = 8.0)
```

@@

Supplementary Figure 3a
CODE running, need to extend the PCA analysis folder
dir_out <- "/home/common/data/output/projects/ENDO/E044/A072/allcells_EndoAtlas_SCTassay/"

```{r}

p <- readRDS(paste0(dir_ENDO,"_Data/03_PCA_analysis/p_EndoAtlas.rds"))
